## NCAA Football Attendance

Let's load the tidyverse.

```{r}
library(tidyverse)
```

And read in the attendance data:

```{r}
attendance <- read_csv("https://dwillis.github.io/sports-data-files/attendance.csv")
```

Using the tidyverse's `pivot_longer` function, turn the currently wide data into longer data and save it as a new dataframe called `attendance_longer`:

```{r}
attendance_longer <- attendance |> pivot_longer(cols = starts_with("20"), names_to = "Year", values_to = "Attendance")

attendance_longer |> filter(Attendance >= 500000)  |>
  group_by(Institution) |>
  summarise(years = n()) |>
  filter(years < 5)

```

Let's try to figure out whether football attendance has returned to "normal" by 2023, defining "normal" as 2019 figures. For that we'll need to isolate those two years using `filter()` and get rid of any NAs:

```{r}
attendance_two_years <- attendance_longer |> filter(Year %in% c(2019, 2023)) |> na.omit()
```

Now, in order to calculate a percentage change between those two years, we'll need to go back to wider data and again ditch teams where we don't have both years:

```{r}
attendance_wide <- attendance_two_years |> pivot_wider(names_from = Year, values_from = Attendance) |> na.omit()
```

Finally, we'll add a percentage change column to that dataframe (remember, it's (New-Old)/Old) and arrange it to see the results.

```{r}
attendance_wide <- attendance_wide |> mutate(percent = (`2023`-`2019`)/`2019`*100)
```

Some of these clearly are influenced by performance on the field. Below, describe the most interesting results (positive or negative) and what you think might be going on with them. Feel free to do some googling and describe what other data would be helpful to clarify what the best stories here might be. What surprises you about these results?

**ANSWER**
With three MAC teams in the bottom seven for a decrease in attendance from 2019 to 2023, did the switch to move most of its conference games to weeknights hurt attendance? The conference is making more money from a TV deal to play games during the week, but did that prohibit fans from attending games on weeknights? 

```{r}
big_ten_with_wins <- read_csv("https://dwillis.github.io/sports-data-files/big_ten_no_2020.csv")
```
```{r}
big_ten_averages <- big_ten_with_wins |>
  group_by(Institution) |>
  summarise(
    avg_attendance = mean(Attendance),
    avg_wins = mean(Wins),
    sd_attendance = sd(Attendance),
    sd_wins = sd(Wins)
  )
```
ANSWER - Northwestern averages the worst attendance in the conference despite winning an average of six games a year, which can be considered a good season because of bowl eligibility. Nebraska averages the fourth-best attendance in the conference while only winning around five games a year, which is less than Northwestern. Is this because Nebraska has a bigger stadium compared to Northwestern, or does Nebraska's history of success drive people to show up to every game regardless of the product on the field?
