```{r}
library(tidyverse)
```

```{r}
matches23 <- read_csv("https://raw.githubusercontent.com/dwillis/NCAAWomensVolleyballData/main/data/ncaa_womens_volleyball_matchstats_2023.csv")

matches24 <- read_csv("https://raw.githubusercontent.com/dwillis/NCAAWomensVolleyballData/main/data/ncaa_womens_volleyball_matchstats_2024.csv")


```
Get Maryland's aces

```{r}
matches23 |> filter(team == 'Maryland Terrapins, Terps')|>
  group_by(result) |>
  summarise(
    avg_aces = mean(aces)
  )

matches24 |> filter(team == 'Maryland Terrapins, Terps')|>
  group_by(result) |>
  summarise(
    avg_aces = mean(aces)
  )
  
```

T-test for significance
null hypothesis: There's no difference between the two years
```{r}
umd_aces23 <- matches23 |> filter(team == 'Maryland Terrapins, Terps')|> mutate(season=2023) |> filter(date < '2023-09-12')
umd_aces24 <- matches24 |> filter(team == 'Maryland Terrapins, Terps')|> mutate(season=2024)

result <- t.test(umd_aces23$aces, umd_aces24$aces, alternative="two.sided", var.equal = TRUE)

print(result)
```


ANOVA
```{r}
combined <- bind_rows(umd_aces23, umd_aces24)

combined$result <- factor(combined$result)
combined$season <- factor(combined$season)

anova_result <- aov(aces ~ result * season, data=combined)

summary(anova_result)
```












Here's an example of how to calculate z-scores using NCAA volleyball teams. We'll use match data for the 2023 season.

```{r}
matches <- read_csv("https://raw.githubusercontent.com/dwillis/NCAAWomensVolleyballData/main/data/ncaa_womens_volleyball_matchstats_2023.csv")
```

### Isolate the columns we might want to use for our metrics

```{r}
teamquality <- matches |> 
  select(team, kills, s, errors, total_attacks, assists, s_err, digs, ret_att, r_err, b_err)
```


### Calculate averages

```{r}
teamtotals <- teamquality |> 
  group_by(team) |> 
  summarise(
    avg_kills = mean(kills),
    avg_errors = mean(errors),
    avg_attacks = mean(total_attacks),
    avg_assists = mean(assists),
    avg_s_err = mean(s_err),
    avg_digs = mean(digs),
    avg_ret_att = mean(ret_att),
    avg_r_err = mean(r_err),
    avg_b_err = mean(b_err)
  )
```

### Create Z-Scores

```{r}
teamzscore <- teamtotals |> 
  mutate(
    kills_zscore = as.numeric(scale(avg_kills, center = TRUE, scale = TRUE)),
    errors_zscore = as.numeric(scale(avg_errors, center = TRUE, scale = TRUE)) * -1,
    s_err_zscore = as.numeric(scale(avg_s_err, center = TRUE, scale = TRUE)) * -1,
    digs_zscore = as.numeric(scale(avg_digs, center = TRUE, scale = TRUE)),
    TotalZscore = kills_zscore + errors_zscore + s_err_zscore + digs_zscore
  )
```

### Look at the results

```{r}
teamzscore |> select(team, TotalZscore, kills_zscore, errors_zscore, s_err_zscore, digs_zscore) |>  arrange(desc(TotalZscore))
```



### z-score analysis assignment

```{r}
matches_2024 <- read.csv("https://raw.githubusercontent.com/dwillis/NCAAWomensVolleyballData/main/data/ncaa_womens_volleyball_matchstats_2023.csv")
glimpse(matches_2024)
```

```{r}
teamtotals_2024 <- matches_2024 |> 
  group_by(team) |> 
  summarise(
    avg_errors = mean(errors),
    avg_kills = mean(kills),
    avg_digs = mean(digs),
    avg_aces = mean(aces),
    avg_hit_pct = mean(hit_pct),
    avg_sets = mean(s)
  )
```
ANSWER - I chose to include a team's average offensive stats of kills, digs, aces and hit percentage. I incorporated these stats into the composite z-score because I feel this shows us a good benchmark as to who are the best offensive teams, meaning they score more points than others. I included the average number of errors for each team because successful teams tend to make fewer errors than less successful teams, and including the number of sets each team plays can show which teams are dominant and win in less played sets than other teams.



```{r}
teamzscore_2024 <- teamtotals_2024 |>
  mutate(
    errorszscore = as.numeric(scale(avg_errors, center = TRUE, scale = TRUE)),
    killszscore = as.numeric(scale(avg_kills, center = TRUE, scale = TRUE)),
    digszscore = as.numeric(scale(avg_digs, center = TRUE, scale = TRUE)),
    aceszscore = as.numeric(scale(avg_aces, center = TRUE, scale = TRUE)),
    hitpctzscore = as.numeric(scale(avg_hit_pct, center = TRUE, scale = TRUE)),
    setzscore = as.numeric(scale(avg_sets, center = TRUE, scale = TRUE)),
    TotalZscore = errorszscore + killszscore + digszscore + aceszscore + hitpctzscore + setzscore
  ) |> ungroup() |> arrange(desc(TotalZscore))
```

ANSWER - Based on the statistics I used, the best team in NCAA volleyball in 2024 so far is LIU with a total z-score of 7.6. The best power-4 team is California with a z-score of 4.9, and Maryland ranks as one of the worst teams so far this year with a -3.1 z-score.

A possible story I found from this data set is that the best teams on the z-score scale are some of the best serving teams in the country in terms of aces. Three of the first five team on the z-score scale average over seven aces a match, while the lowest average in college volleyball is Hampton at 2.7. A story could dive into the best serving teams and how they are able to win points quick and efficiently, leading to less errors during matches.

Another story idea I discovered is that errors might not have as big of an impact as I initially thought. St. Peter's, who has the sixth highest z-score, commits an average of over 23 errors per game. Teams like Wisconsin average only 12. So despite committing a plethora of errors, it doesn't seem to effect teams like St. Peters who rank high in the z-score composite ranks.


###Z-Score Write Up

Teams that commit more errors on average than other teams typically don't see an impact, meaning errors aren't as big of a deal as team's make it out to be.

The team with the lowest average of total errors -- which combines errors like service errors, receiving errors and blocking errors -- was Wisconsin, who averages just over 12 errors a match. Idaho averages the worst, more than doubling Wisconsin's total and averages over 25 a outing.

But total errors isn't the biggest stat that dictates how well a team performs, and they become inconsequential when used with other statistics.

Saint Peters, who averages the third-highest average of total errors of around 23, makes up for its misfortunes by achieving high averages in aces with over five per match, the fifth-best mark in the country. It also boasts a decent attack, notching a high average in kills and a fair average hitting percentage.

How many errors a team commits is useful to see who is wasteful with its opportunities. But, some teams are better at combating their mistakes by being above average in other categories, like aces and kills.


###Dumbbell and lollipop charts

```{r}
library(tidyverse)
library(ggalt)
```

```{r}
logs <- read_csv("https://dwillis.github.io/sports-data-files/ncaa_womens_volleyball_matchstats_2023.csv")
```

```{r}
big10 <- c("Nebraska Huskers", "Iowa Hawkeyes", "Minnesota Golden Gophers", "Illinois Fighting Illini", "Northwestern Wildcats", "Wisconsin Badgers", "Indiana Hoosiers", "Purdue Boilermakers", "Ohio St. Buckeyes", "Michigan Wolverines", "Michigan St. Spartans", "Penn St. Nittany Lions", "Rutgers Scarlet Knights", "Maryland Terrapins, Terps")

errors <- logs |>
  filter(team %in% big10) |> 
  group_by(team) |> 
  summarise(
    total_errors = sum(errors), 
    opp_errors = sum(defensive_errors))
```

```{r}
ggplot() + 
  geom_dumbbell(
    data=errors, 
    aes(y=team, x=total_errors, xend=opp_errors)
  )
```

```{r}
ggplot() + 
  geom_dumbbell(
    data=errors, 
    aes(y=team, x=opp_errors, xend=total_errors),
    size = 1,
    colour = "grey",
    colour_x = "red",
    colour_xend = "green") +
  theme_minimal()
```

```{r}
ggplot() + 
  geom_dumbbell(
    data=errors, 
    aes(y=reorder(team, opp_errors), x=opp_errors, xend=total_errors),
    linewidth = 1,
    color = "grey",
    colour_x = "green",
    colour_xend = "red") + 
  theme_minimal()
```

```{r}
ggplot() + 
  geom_lollipop(
    data=errors, 
    aes(y=team, x=opp_errors), 
    horizontal = TRUE
    )
```

```{r}
md <- errors |> filter(team == "Maryland Terrapins, Terps")

ggplot() + 
  geom_lollipop(
    data=errors, 
    aes(y=reorder(team, opp_errors), x=opp_errors), 
    horizontal = TRUE
    ) + 
  geom_lollipop(
    data=md,
    aes(y=team, x=opp_errors),
    horizontal = TRUE,
    color = "red"
  ) + 
  theme_minimal() + 
  labs(title = "Maryland middle of the pack among Big Ten teams", y="team")
```