```{r}
library(tidyverse)
library(postmastr)
library(rvest)
library(ggplot2)
library(scales)
library(gt)
library(waffle)

msoc_div1_all <- read_csv("msoc_div1_all.csv")
```

###Cleaning player heights
  ##Need to finish with players who don't have height listed on profile
```{r}
msoc_div1_all <- msoc_div1_all |>
  mutate(HeightCleaned = case_when(
    height %in% c("5\'4\"", '5-4', "5\' 4\''") ~ "\'5-4\'",
    height %in% c("5\'2\"", '5-2', "5\' 2\''") ~ "\'5-2\'",
    height %in% c("5\'5\"", '5-5', "5\' 5\''") ~ "\'5-5\'",
    height %in% c("5\'3\"", '5-3') ~ "\'5-3\'",
    height %in% c("5\'9\"", '5-9', "5\' 9\''") ~ "\'5-9\'",
    height %in% c("5\'6\"", '5-6', "5\' 6\''") ~ "\'5-6\'",
    height %in% c("5\'7\"", '5-7', "5\' 7\''") ~ "\'5-7\'",
    height %in% c("5\'8\"", '5-8', "5\' 8\''") ~ "\'5-8\'",
    height %in% c("5\'10\"", '5-10', "5\' 10\''") ~ "\'5-10\'",
    height %in% c("5\'11\"", '5-11', "5\'111\"", "5\ 11\''", "5\' 11\''", "5\' 11\"") ~ "\'5-11\'",
    height %in% c("6\'0\"", '6-0', "6\' 0\''") ~ "\'6-0\'",
    height %in% c("6\'1\"", '6-1', "6\' 1\''") ~ "\'6-1\'",
    height %in% c("6\'2\"", '6-2', "6\' 2\''") ~ "\'6-2\'",
    height %in% c("6\'3\"", '6-3', "6\' 3\''") ~ "\'6-3\'",
    height %in% c("6\'4\"", '6-4', "6\' 4\''") ~ "\'6-4\'",
    height %in% c("6\'5\"", '6-5', "6\' 5\''") ~ "\'6-5\'",
    height %in% c("6\'6\"", '6-6', "6\' 6\''") ~ "\'6-6\'",
    height %in% c("6\'7\"", '6-7', "6\' 7\''") ~ "\'6-7\'",
    height %in% c("6\' 8\''") ~ "\'6-8\'"
  ))

```

###Cleaning player classes
  ##All Cleaned
```{r}
msoc_div1_all <- msoc_div1_all |>
  mutate(ClassCleaned = case_when(
    class %in% c('Fr.', 'R-Fr.', 'FR', 'Freshman', 'Redshirt Freshman', 'Fy.', 'FY', 'Rf.', 'Fy') ~ 'Freshmen',
    class %in% c('So.', 'R-So.', 'SO', 'Sophomore', 'Redshirt Sophomore', 'RS So.') ~ 'Sophomore',
    class %in% c('Jr.', 'R-Jr.', 'JR', 'Junior', 'Redshirt Junior', 'R-Jr', 'RS JR') ~ 'Junior',
    class %in% c('Sr.', 'R-Sr.', 'SR', 'Senior', 'Redshirt Senior') ~ 'Senior',
    class %in% c('Gr.', 'R-Gr.', 'GR', 'Grad.','Graduate Student', 'Redshirt Graduate Student', 'Fifth Year', '5th', '6th', 'Sr.+', '5th.') ~ 'Graduate Student',
    name %in% c('Henrik Weiper') ~ 'Junior',
    name %in% c('Iyke Dafe', 'Lorenzo Amaral', 'Carlo Brown', 'Shayne Thompson', 'Zion Wharton', 'Heechan Han', 'Diego Elizalde', 'Carter Smith') ~ 'Sophomore',
    name %in% c('Tanner Barry', 'Harri Sprofera', 'Jack Cloherty', 'Keegan Walpole', 'Mike Balleani', 'Gavin Tabije', 'Kyle Gee', 'Cal Walsh') ~ 'Senior',
    name %in% c('Taha Kina', 'Scott Gustafson', 'Charlie Adams', 'Levi Pillar') ~ 'Graduate Student',
    name %in% c('Jamin Gogo Peters', 'Mads Stistrup Petersen', 'Langdon Gryglas', 'Dylan Ellis', 'Adolfo Diaz', 'Greyson Mitchell') ~ 'Junior',
    name %in% c('Timi Browne', 'Andre Romo', 'Stefano DAgostini', 'Amoni Thomas') ~ 'Freshmen'
  ))

msoc_div1_all |>
  group_by(ClassCleaned) |>
  summarise(
    total = n()
  )
```
-Freshmen is the most represented class, sophomore and junior are seperated by just two players.
- Seems once a player plays one or two seasons, they look for other opportunities outside of the college game

###Next Steps
I think for this part of the presentation I want to focus on player positions. I want to see if there are trends, like taller players as goalies or a certain class being a bulk of a position group.

From there, I want to look into the player position and continent data to see if one continent or country produces the most players for a certain position. I would love to show this data off in a map -- my initial thoughts were a map of each continent for each position group where a country is filled in, either light or dark, based on the number of players from each country. My next step will be working with the right package for making maps to display the player position data.

```{r}
write_csv(msoc_div1_all, "msoc_div1_all.csv")
```



###Cleaning player positions
  ##Cleaned all players with listed positions
```{r}
msoc_div1_all <- msoc_div1_all |>
  mutate(PositionCleaned = case_when(
    name %in% c('Nikola Djordjevic') ~ 'Defense',
    position %in% c('Goalkeeper', 'GK', 'GOALKEEPER', 'G', 'Goaltender', 'Goal Keeper') ~ 'Goalie',
    position %in% c('Forward', 'Attack', 'F', 'FORWARD', 'F/FM', 'Striker', 'Winger-Forward', 'Winger', 'W', 'Wing', 'Foward') ~ 'Forward',
    position %in% c('Midfield', 'M', 'MIDFIELD', 'Midfielder', 'Central Midfielder', 'MF', 'CAM', 'Left Midfielder', 'Center Midfielder', 'Midfielder (Captain)') ~ 'Midfield',
    position %in% c('Defender', 'D', 'DEFENSE', 'Defense', 'Back', 'B', 'F/B', 'CB', 'LCB', 'Center Back', 'Outside Back', 'Left Back', 'Center/Left Back', 'Defense (Captain)', 'Centerback', 'Defender/Center Back') ~ 'Defense',
    position %in% c('Midfielder/Defender', 'D/M', 'B/M', 'Defender/Midfielder', 'M/D', 'MF/D', 'D/MF', 'Defender / Midfielder', 'Midfielder / Defender', 'Defense/Midfield', 'Midfield/Back', 'Defender/Midfielder (Captain)', 'Midfield/Defense (Captain)', 'Midfield/Defense', 'Midfielder/Back', 'Midfielder/Defense', 'Defense/Midfielder', 'Defender/Midfield', 'Midfield/Defender', 'Defender/Midfield', 'Defender/ Midfielder', 'Midfield / Defense', 'Defense / Midfield') ~ 'Midfield/Defense',
    position %in% c('F/M', 'Forward/Midfielder', 'Midfielder/Forward', 'MF/F', 'M/F', 'F/MF', 'For./Mid', 'FWD/MID', 'Forward/Midfield', 'Forward / Midfielder', 'Midfield/Forward', 'Midfielder / Forward', 'Midfielder-Striker', 'Forward/ Midfielder', 'Midfielder/ Forward', 'Forward / Midfield') ~ 'Forward/Midfield',
    position %in% c('F/D', 'Defender/Forward', 'Forward/Defense', 'Forward / Defender', 'Defender/Winger', 'Defense/Forward') ~ 'Forward/Defender',
    name %in% c('Alex Yagudayev', 'Sebastian Cutler DeJesus', 'Connor Margo', 'Jordaine Jaeger', 'Martin Dominguez', 'Cameron Victor', 'Rob Gjelaj', 'Ethan Kornas', "'Patrick O'Day'", 'Zackary Kacic', 'Tyler Brennan', 'Bennet Glinder', 'Aurie Briscoe', 'Ciaran Dalton', 'Graham Kois', 'Andrew  Noel', 'Phillip Falcon III', 'Aidan Coffey', 'David Howard', 'Mateus Ruiz-Hurst', 'Joshua Moya', 'Juan Martinez', 'Mattia Marsili', 'Rikiya Ura', 'Jakub Grzesiak', 'Joao Mesquita', 'Landon Barth', 'Julian Marcos', 'Jacob MacDonald', 'Rex Flanagan', 'Gavin Pennell', 'Ittetsu Hirai', 'Philip Hovers', 'Ryan Swan', 'Ky Mani Dade', 'Massimo Oedekoven Pomponi', 'Dillan Danks', 'Ryan Haskell', 'Dylan Van der Walt', 'Nathen Jones', "'Connor O'Keefe'", 'Alex Bobocea', 'Ryan Gross', 'Blake Koski', 'Anton Kinnunen', 'Jaron Noble', 'Brian Garcia', 'Benjamin Miller', 'Alejandro De La Torre', 'Kevin Dabrowski', 'Asaf Kristal', 'Joey Galante', 'Luca Ulrich', 'Tenzing Manske', 'Charlie DeMarco', 'Max Miller', 'Aaron Salinas', 'Ivan Horvat', 'Andrew Laplaca', 'Francisco Ranieri', 'Nacho Alfaro', 'Zac Clary', 'Thomas Wallis', 'Beltran Fernandez', 'Nigel Van Haveren', 'Sam McGee', 'Marc Kouadio', 'Anton Ottesen', 'Max Kaplan', 'Will Bowers', 'Ryan Gallagher', 'Wessel Speel', 'Carson Jeffery', 'Tommy Williams', 'Tomas Butkovic', 'Quinn Millerd', 'Eoin Kennedy', 'Brandon  Limes', 'Joshua Naumoff', 'Nicky McCune', 'Ben Oetman', 'Dylan Glowaski', 'Andres Rosales') ~ 'Goalie',
    name %in% c('Balthi Saunders', 'Jasper Zulman', 'Marcello Mazzola', 'Vincent  Petrera', 'Javon Daniels', 'Colby  Raymond', 'Milton Lopez', 'Chris Deamon', 'Dominic Bartoni', 'Stephan Soghomonian', 'Oliver Knotek', 'Jacobo Sanfeliu', 'Pavel Dashin', 'Nacho Abeal', 'Jacob Bilyeu', 'Ryley Gibbs', 'Mario Navarro Perez', 'Ian Abbey', 'Anthony  Morano', 'Nico Rosamilia', 'Ola Maeland', 'Eddie Krupski', 'Matty Lynch', 'Stas Korzeniowski', 'Jack Wagoner', 'Romeo Dahlen', 'Brandon Curran', 'Carter Haynes', 'Adam Kuechler', 'Vinzent Zingel', 'Alberto Cruz', 'Kai Sullivan', 'Ezekiel Padilla', 'Zion Vaughn', 'Elvin Maldonado', 'Abdullahi Mohamed', 'Damani Harris', 'Luis Flores', 'Jack Bratcher', 'Jose Estrada', 'Roman Hemphill', 'Omar Mora', 'Colin Spuler', 'Pato Padilla', 'Pierre Ulloa', 'Ali Taleb', 'Theo Klein', 'Wawa Palga', 'Bobby Marsteller', 'Ethan Glaser', 'Timmy Barlow', 'Garrett Potts', 'Donghyun Kim', 'Simon Lugo', 'Abou Cherif', 'Hakeem Morgan', 'Anthony Wilson', 'Alejandro Fuentesal-Atalaya', 'Kayvon Monfared', 'Josh Elash', 'Marco Byers-Mora', 'Nacho Macias', 'Cole McEvoy', 'Rolando Onu', 'Caden Stafford', 'Jake Sweeney', 'Ólafur Darri Sigurjónsson', 'Steven Ozga', 'Seth Powder', 'Charlie Herley', 'Tommy Zipprich', 'Perry Kingson', 'Thomas Robertson', 'Bora  Turker', 'Ryan Mundy', 'Edgar Soto', 'Yusuff Ojebode', 'Fransicso "Paco" Segura', 'Josiah "Jo" Henderson', 'Cristian Mendoza', 'Emanuel "Manny" Martinez', 'Diego Muller', 'Diego Robles', 'Sello Diphoko', 'Chase Ashby', 'Jack Finnegan', 'Joshua Torres', 'Brian Perez', 'Jesse Anamoo', 'Andres Lemus', 'Jaiden Ramsay-Kelly', 'Omar Thompson', 'Marlon Tabora', 'Ronan Dillow', 'Mitchell Baker', 'Jordi Sada-Paz', 'Wilfer Bustamante', 'Ryan Reid', 'Jackson Price', 'Christian  Kraus', 'Oliver Moller-Jensen', 'Andreas Raisanen', 'Noah  Kvifte', 'Aboubacar Traore', 'Mamadou Diarra', 'Bernardo Dos Santos Monteiro', 'Eduardo Mustre', 'Michael Appiah', 'Enrique Mutsoli', 'Prince Ngeleka', 'JP Ozuna', 'Ron Arie', 'Gabriel Ramos', 'Abdi Bahur', 'Lucas Nordin', 'Noah Franks', 'Jimmy Choi', 'Zayd Idlibi', 'Adrian Byasiima', 'Adam Luckhurst', 'Sol Arbib', 'Evan Carlson', 'Snorre Espersen', 'Saiheed Jah', 'Eloge Iradukunda', 'Zacarias Escobar-Bowie', 'Mario Carlos', 'Sulaiman Bah', 'Jedidiah  Griffin', 'Fitz Williams', 'Julian Varela', 'Jackson Kestler', 'Conner Lisenbee', 'Oren Stuppel', 'Armin Tehrani', 'Ashton Alonge', 'Colin Pearce', 'Sean McTague', 'Luke Schaefer', 'Finn Linas', 'Roman Anast', 'Brendan Cunningham', 'Hadar Lavinsky') ~ 'Forward'
))
```

##HOLD - DO NOT DELETE

    name %in% c('Diego Valles', 'Mikhail Zaretser', 'Jordan Canica', 'Jason Bouregy', 'Jorge Garcia', 'Branden Johns', 'Kyle Dixon', 'Michael teDuits', 'Josh Oladele', 'Karson Vazquez', 'Alex Salvo', 'Niv  Berkovitz', 'Richard Garcia', 'Jaylinn Mitchell', 'Daniel Escorcia', 'Hannes Ottoson', 'Ibrahim Keita', 'Christian Chandler', 'Noah Ervin', 'Carles Zomeno', 'Yasha Schaerer', 'Zach Renz', 'Ben Perkins', 'Brian Franco', 'Tyler Sargent', 'Ryan Lim', 'Alejandro Perez Jorda', 'Campbell Stalker', 'Olafur Freysson', 'Cole Hellert', 'Anthony Rouse', 'Zach Gardner', 'Tomislav Vrdoljak', 'Joseph DiPreta', 'Christian Amaral', 'Ben Biton', 'Mark Cajamarca', 'Lee Mara', 'Nick  Fernandes', 'Cole Cruthers', 'Curt Calov', 'Thomas Angelone', 'Dylan  Carlson', 'Nestor Cabrera', 'Francesco  Di Ponzio', 'Kristófer Arnarsson', 'Gavin Seele', 'Aaron Messer', 'Jack-Ryan Jeremiah', 'Erickson Sakalosky', 'Marco Bottene', 'Charlie Gaffney', 'Mathis Varin', 'Pierce Wagner', 'Tim Shine', 'Aiden Frick', 'Patrick Cayelli', 'Will Kelly', 'Bele Alomerovic', 'Danny  Govea', 'Luca Baltzer', 'Jose Maria Barrera', 'Massimo Erfani', 'James Andrew', 'Carlos Maldonado', 'Jorge Galvan', 'Emmanuel Dennis', 'Mateusz Flak', 'Thiago Patto', 'Juan Moreno', 'Joao Rosito', 'Tweneboa Kodua', 'Nikola Slijivic', 'Jedidiah Kampamba', 'Benjamin Morgan', 'Tommy Lamb', 'Tony Shaw', 'Diego Hoenderkamp', 'Josh Line', 'Junior Casillas', 'Shachar Nissim', 'Brooks Beeman', 'Stanley Bazelais', 'Victor Labite', 'Fabian Perez', 'Graham Dougald', 'Dominik Topolsky', 'Anthony Fanelli', 'Christian Rodriguez', 'Luciano Schiaffini', 'Jamie Benayon-Abraham', 'Erick Villatoro', 'Junee Lee', 'Evan Gaines', 'Rowen Choi', 'Danny Chettri', "'Eliot O'Neil'", 'Kai Reece', 'Jastej Gill', 'Hugo Tavares', 'Steven Anderson', 'Okeefe Cunningham', 'Mydas Smalls', 'Braden Fidelak', 'Daniel Idiakhoa', 'Noah Robertson', 'Gael Quintero', 'Minki Jeong', 'Leo Marques de Costa', 'Quinn Galvin', 'Reagan Heslin', 'Sean McEvoy', 'Richie Nichols', 'Cody Angelini', 'Ben Schouten', 'Tyler Flynn', 'Juston Rainey', 'Tyler Tucker', 'Noah Levy', 'Jason Pynadath', 'Athanasios Cosse', 'Yusef Gueye', 'Giacomo Zizza', 'Kent Neureiter', 'Connor  Kuenstle', 'Aiden Gonzalez', 'Daniel Ordonez', 'Tatenda Chigede', 'Luis Zuniga', 'Peleg Armendariz', 'Santiago Ruiz', 'Erick Rios', 'Dylan Navarijo', 'Timothy Ospina', 'Cesar "Danny" Elizalde', 'Miles Merritt', 'Rui Reis', 'Preston Huitron', 'Carlos Nevarez', 'Max Aquino', 'Andi Kallaba', 'Alan Alonso', 'Jorge Hernandez', 'Bor Zunec', 'Morgan Worsfold-Gregg', 'Simeon Dishman', 'Rio Pemberton', 'Freddy Ferguson', 'Jake Salas', 'Cezar Onut', 'Eric Howard', 'Diego Letayf', 'Max Viera', 'Joe Buck', 'Mateo Ponce Ocampo', 'David Urrutia', 'Blaine Mabie', 'Aidan Godinho', 'Cole Parete', 'Jack Brown', 'Julian Barrios Cristales', 'Zach Zengue', 'Matthew Helfrich', 'Zayan Ahmed', 'Jack Heaps', 'Matthew Van Horn', 'Trip Campbell', 'Ivan Agyaakwah', 'Ben Boxall', 'Diego Hernandez', 'Caleb Johnson', 'Wesley Goodwin', 'Miguel Sosa', 'Landon Hill', 'Christian  Kraus', 'Luke Hutzell', 'Beck Dean', 'Malachi Grant', 'Samir  Spaulding', 'Mark Andros', 'Thiago Pires', 'Jeremy  Montero', 'Jeremy  Montero', 'Arthur Widiez', 'Ajay Stewart', 'Matthew  Alfred', 'Zach Hassell', 'Joep Wouters', 'Sebastian Zettl', 'Noel Williamson', 'Tyrese  Small', 'Ethan Schumaker', 'Mathys Lefebvre', 'David Boccuzzo', 'Diego Castillo', 'Juan Pablo Correa', 'Nicolas Villalobos', 'Driss Nasser', 'Julien Gastaldy', 'Adrian Ebersbach', 'Ulysses Hendriks', 'Gabriel Betancourt', 'Louie Salkeld', 'Ingvar Kolbjornsen', 'Oliver Einarsson', 'Elijah Lynch', 'Rodrigue Moussa', 'Matias Delellis', 'Shewit Worton', 'Jamie Kabussu', 'Trevor Burns', 'Jack Zugay', 'Julius Suber', 'Caleb Donaldson', 'J.P. Pascarella', 'Barrett Kitts', 'Kai Knuchel', 'Damian Segura', 'Jackson Kirsch', 'Dalton Visconti', 'Matthew Sacristan', 'Matthias Heiland', 'Erick Serrano', 'Fernando Valenzuela', 'Cesar Aubour', 'Jose de la Torre', 'Jonathan Grado', 'Damian Espinoza', 'Alix Soukup', 'Roberto Ordonez', 'Jorge Quintero', 'Diego Guerra', 'Rylan Firouznam', 'Jackson Miller', 'Nate Colley (C)', 'Quinn Mahoney', 'Bakuena Ramakatsa', 'Benji Jimenez', 'Kai Pope', 'Michael Oelberger', 'Gaven Egan', 'Evans Dapaah') ~ 'Midfield',
    name %in% c('Tommy Johnson', 'Lorenzo Avalos', 'Luke Haggerty', 'Cam Tolson', 'Will Spitznagle', "'O'Neil Dawes'", 'Cole Knapp', 'Luke Martelli', 'Brock Pope', 'Cesar Ruvalcaba', 'Yves Vaage', 'Owen Zarnick', 'Kyran Chambron Pinho', 'Lamar Bynum', 'Enzo Panozzo', 'Mason Grimm', 'Ryan Clanton-Pimentel', 'Charlie Isphording', 'Elliott Forestier', 'Wes Gibson', 'Archie McDonnell', 'Enrique Ezquerro', 'Patrick Coleman', 'Bobby Pauly', 'Nic Muench', 'Anton Mosley', 'Garrison Hill', 'Colin Bastianoni', 'Jesper Schone Vogtengen', 'Dren Dobruna', 'Thomas Sams', 'Miguel Plaza', 'Henrik Winkelmann', 'Alexander Zielonka', 'Eric Svensson', 'Benjamin Fogarty', 'Sawyer Koza', 'Devon  Stopek', 'Nick Collins', 'Arnar  Adalsteinsson', 'Scott Godden', 'Joey Zalinsky', 'Aidan Flynn', 'Erick  Ruiz', 'Bryan Keating', 'Leo Burney', 'Oliver Pratt', 'Joaquin Niehenke', 'Ben Do', 'Malachi Neal', 'Connor Dawson', 'Nik Kathiresan', 'Sean Jennings', 'Owen Sullivan', 'Patrick Weir', 'Carter Feinman', 'Emmanuel Obiefuna', 'Lukas Aeberli', 'Nicholas Engels', 'Javier Chavez', 'Lennart Poth', 'Amado  Negron Gonzales', 'Matteo Carbone', 'Jacob Heisner', 'Ignacio Flores III', 'Miguel Londono', 'Jaxson Stovall', 'Rastko Dekic', 'Baptiste Boit', 'Enzo Gindro', 'Aiden Ussery', 'Schinieder Mimy', 'Steven Boaghe Braniste', 'Chris Sederquist', 'Marshal Minor', 'Joshua Cline', 'Martin Lago', 'Rocco DelGiudice', 'Romario Simpson', 'Figo Cheuk', 'Maks Czyz', 'Antoine DeCoteau', 'Mackie Sacarellos', 'Jayson Salvador', 'Ethan Conway', 'Markus Nilsen', 'Luc Holden', 'Kris Kolar Leban', 'Anthony Cano', 'Adrien Gameiro', 'Tyler Trusner', 'Jayden Gonsalves', 'Nathan Rodrigues', 'Ismail Nieves', 'Mathew Habovstak', 'Carl Olsen', 'Jack Englebert', 'Harrison Vail', 'Pat Kakayira', 'Jordy Luchies', 'Brandon Meminger', 'Chris Ogor', 'Jahvar Stephenson', 'Eddie Smith', 'Jake Mayer', 'Oscar Halls', 'Curtis Wagner', 'Zach Tettemer', 'Kayin Oladinni', 'Chase Dade', 'Sam Davis', 'Trey  Sheeler', 'Fernando Cohate', 'Paul Smajlaj', 'Matthew Aitchison', 'Will Ansah', 'Rochaine Baker', 'Canon Downey', 'Leonardo Aguirre', 'Brady Drozdowski', 'Hazani Torres', 'William  Fagerberg', 'Giovanni Padilla', 'Gianfranco Paladino', 'Paul Brauckmann', 'Luka Bekovic', 'Juan Gutierrez', 'Darien Martin', 'Sebastian Rodriguez', 'Daunte Saunchez', 'Tremain  Simpson', 'Theo Butterworth', 'Ron Pressler', 'Maximus Jennings', 'Oliver Stafford', 'Miles Avery', 'Matiwos Rumley', 'Tate Lampman', 'Reece Fragle', 'Slade Starnes', 'Jack Travis', 'Ryan Wagner', 'Malique Spooner', 'Caleb Chapman', 'Callum Frogson', 'Nick Kinina', 'Matthew  Gordon', 'Kasper Heerfordt', 'Enzo Rabot', 'Jozo Cancar', 'Kerfalla Toure', 'Lucas Christensen', 'Owen Travis', 'David Houja', 'Edgar Aguilar', 'Leo Vilchis', 'Bruno Alcocer', 'Adrian Barosen', 'Joackim Betina', 'Diego Sanchez', 'Dave Neijenhuis', 'Hubert Deragon', 'Ryan Suckling', 'Jason Gun', 'Henrique Cruz', 'Morgan Marvik', 'Agust Arnason', 'Nico Kross', 'Alex Hauschild', 'Niclas Wittur', 'Ryder Barrett', 'Brennan Rzewuski', 'Eskil Gjerde', 'Austin Holtebeck', 'Noah Corrigan', 'Cole Schrage', 'Roi Moskowitz', 'Nick Relerford', 'Giovanni Gloria', 'Julian Borja', 'Tomas Barros', 'Avery Huggins', 'Jalen Belong', 'Justin  Zapata', 'Abraham Gutierrez', 'Logan Mahoney', 'Joaquin Torres', 'Parker Owens', 'Nico Baltazar', 'Ori Bitton', 'Ewan Gordon', 'Jake Oetinger', 'Charlie Hogan', 'Liam Murdin', 'Michael Vick', 'Philip Biondich', 'Manolo Ferreres', 'Trent Lindsey', 'Nick Kashambuzi') ~ 'Defense',
    name %in% c('Foday Bangura', 'Isaac Gugel', 'Jonathan Yowell', 'Matias  Espinar', 'Jack Kehoe', 'Gunnar Caswell', 'James Knowlton', 'Dylan Ellingston', 'Landon  Bealer', 'Alfonso  Young', 'Daniel Ejerenwa', 'Connor Dunnigan', 'Gabe Cox', 'Deng Deng', 'Mitch Williams', 'Aiden Bengard', 'Cole Aman', 'Jack Muoio') ~ 'Midfield/Defense',
    name %in% c('Stephan Moreira', 'Karson Gibbs', 'Lenny Aviles', 'Illia Tyrkus', 'Caleb Frakes', 'Tyler Murphy', 'Sherwin Chen', 'Faqir Raza', 'Lewis Clutton', 'Gennaro Mazzella', 'Beckett Wenger', 'Lloyd Wamu Snell', 'Erich Legut', 'Yanis Rucquois', 'James Saggau') ~ 'Forward/Midfield'
  ))



```{r}
msoc_div1_fixed <- read_csv("msoc_div1_all.csv")

msoc_div1_fixed |>
  group_by(PositionCleaned) |>
  summarise(
    total = n()
  )
```

11/22 UPDATE FOR POSITION DATA:
  - "Nick  Fernandes" not listed on Siena roster (seems to be removed from roster, posted on twitter earlier this year), listed in our data and I placed him under "Midfield" as per last years roster
  - Players are listed as both "Midfield/Defense" and "Defense/Midfield." These players are all listed under "Midfield/Defense"
  - Players with NA (16) for PositionCleaned are either Team Impact or not listed on website roster
  -"MF" on roster data will be listed as MIDFIELDER, not MIDFIELD/FORWARD
  - "W" on roster data will be listed as FORWARD, as "W" stands for WINGER

```{r}
msoc_div1_fixed |>
  group_by(Continent, PositionCleaned) |>
  summarise(
    total = n()
  ) |>
  arrange(desc(total))
  
```

```{r}
msoc_div1_fixed |>
  group_by(Region, PositionCleaned) |>
  summarise(
    total = n()
  ) |>
  arrange(desc(total)) |>
  na.omit()
```

 - Northern Europe leads in defenders, midfielders and forwards and goalies, all four main position groups. I assume that is a large part of the UK, but maybe a map of just the northern European countries I designated would be a good way to show how many players come from the UK and how many come from other countries.
 - Could do a similar map for the other three regions to see if a certain country produces more players from a certain position group than others
 
```{r}
msoc_div1_fixed |>
  filter(Region == 'Northern Europe') |>
  group_by(country, PositionCleaned) |>
  summarise(
    total = n()
  ) |>
  arrange(desc(total)) |>
  na.omit()
```
 


```{r}
msoc_div1_fixed |>
  group_by(HeightCleaned) |>
  summarise(
    total = n()
  )
```
11/22 Update:
  -UAB does not list height on website roster
  -Part of Tulsa roster is unlisted
  -Part of Seton Hall roster is unlisted
  -Still working through all of the heights, but all I have to do for the remaining players is go into the csv file and change from NA to their height

###Next Steps
  - I think the csv file and datawrapper route is the best way to make the maps I want to make. I've used datawrapper before to make maps, so I just have to copy over the csv file I have into datawrapper. Would you suggest a map for each continent, or should I stick to one or two, like Europe and North America?
  - I want to incorporate the heights into the analysis, seeing if there is a possible link between taller players being defenders/goalies or shorter players playing in more attacking positions. Or seeing if certain teams have a tendency to play taller players at those positions compared to other teams.
  - I think there is a story with the position data, especially for players from Northern Europe. England leads in three groups, but Norway, Sweden and Denmark are high up on the list.
  

###12/2 UPDATE


I've cleaned the positions for each player, but now I'm still wondering how the position data is spread around each country, specifically Europe. Defenders and midfielders are the most common while England and Germany produce the most players from those position groups.
```{r}
msoc_div1_europe <- msoc_div1_fixed |>
  group_by(country) |>
  filter(Continent == "Europe") |>
  summarise(
    total = n()
  )
  
```

Defenders and midfielders are the two most common positions to be represented by players from European countries. From those top two position groups to forwards, there is almost a 200 player difference. When teams look for international players that can play on the defensive end of their formations, players from Europe are the most common to fill those spots.

The one player listed at a forward or defender, Ken Raghoebar from the Netherlands who plays for Jacksonville, is a player that most likely plays as a winger or fullback and can play in the wider areas of the formation.
```{r}
msoc_div1_postotals <- msoc_div1_fixed |>
  filter(Continent == "Europe") |>
  group_by(Continent, PositionCleaned) |>
  summarise(
    total = n()
  ) |>
  arrange(desc(total))

ggplot() + 
  geom_bar(
    data=msoc_div1_postotals, 
    aes(x=reorder(PositionCleaned, total),
        weight=total)) + 
  scale_y_continuous(labels=comma) + 
  theme_minimal() + 
  coord_flip()
```

Looking at just players from Europe, I broke down each player into groups based on what country they are from and what position they play. England, Germany and Spain have the most players, with defenders being the most popular position for England and Germany. Germany represents 80 Division I defenders, the most players for a certain position for any European country, while 69 players from England are defenders. Germany also has more goalies than any other country with 24.

Albania's lone Division I player plays in the midfield, as does the only player from Monaco, the Isle of Man and Romania.
```{r}
msoc_div1_positions <- msoc_div1_fixed |>
  group_by(PositionCleaned, country) |>
  filter(Continent == "Europe") |>
  summarise(
    total = n()
  )

ggplot() + 
  geom_bar(
    data=msoc_div1_positions, 
    aes(x=reorder(country, PositionCleaned),
        weight=total, 
        fill=PositionCleaned)) + 
  coord_flip()
```


With there being so many defenders from Europe, my next step is to finish cleaning the heights of every player to see if there is a consistent height. Once I complete the height cleaning for every player, I can see if the average height is taller than players that play in the midfield or attack, which I assume it will be.

I am also going to make a choropleth map in datawrapper for Europe to show the number of players from each country. When I make the map, how will I be able to import it into R?

```{r}
msoc_div1_fixed |>
  group_by(Continent) |>
  summarise(
    total = n()
  )
```

```{r}
msoc_div1_fixed |>
  group_by(team) |>
  summarise(
    total = n()
  )
```



```{r}
msoc_div1_new <- read_csv("~/Downloads/MSOC Roster Data - Roster Data.csv")

msoc_div1_new |>
  group_by(PositionCleaned) |>
  summarise(
    total = n()
  )
```

```{r}
msoc_div1_all |>
  group_by(Continent) |>
  summarise(
    total = n()
  )
```


